Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-04-29 concurrency/CONCUR 2023/paper.tex
continue to restructured sections

\authorrunning{Duc Than Nguyen and William Mansky} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

@@

@@

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% inRange for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn->n}\mapsto\texttt{(t, lock, min, max)} 
			\end{array}
			\right\}
		}
		\\ 
		\texttt{inRange(pn, k)} 
		\\
		{\color{blue}
			\left\{\exists \  \texttt{res.}
			\begin{array}{c}
				\ \texttt{pn->n}\mapsto\texttt{(t, lock, min, max)} \  \\ 
				\ \ast  \ \texttt{(if res then } \texttt{(min < k < max)} \texttt{ else } \texttt{(k} \leq \texttt{min} \lor \texttt{k} \geq \texttt{max))}
			\end{array}
			\right\}
		}
		\\
		\\
		%insertOp for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t} \  \ast \ \texttt{n}\mapsto\texttt{min} \ \ast \ \texttt{n}\mapsto\texttt{max}
			\end{array}
			\right\}
		}
		\\
		\texttt{insertOp(pn, k, v)}
		\\
		{\color{blue}
			\left\{\exists \ \texttt{t' l r lk1 lk2}. 
			\begin{array}{c}
				\ \texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \\ 
				\ \ast \ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, k))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (k, max))}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specifications of \texttt{inRange} and \texttt{insertOp} for the give-up template}
	\label{fig:inRange_insertOp_giveup}
\end{figure}

The \texttt{inRange} function (Figure \ref{fig:inRange_insertOp_giveup}) simply computes whether the input key \lstinline{k} is in the range \texttt{(min, max)} associated with the node \texttt{n}, and returns 0 or 1 accordingly.

As previously mentioned, the \texttt{insertOp} specification (Figure \ref{fig:inRange_insertOp_giveup}) is slightly different from the lock-coupling version, to account for the added \lstinline{min} and \lstinline{max} fields. In a BST, if the current node's range is \lstinline{(min, max)} and its key is \lstinline{k}, its left child will have range \texttt{(min, k)} and its right child will have range \texttt{(k, max)}. Otherwise, \lstinline{insertOp} behaves identically, storing \lstinline{k} and \lstinline{v} in the current node and creating two empty child nodes.

>>>>

\authorrunning{Duc Than Nguyen et al.} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

@@

\than{Talking about different of \texttt{insertOp} specs here.}

\begin{figure}[h]
	\centering
	\begin{mathpar}
		%insertOp for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t} \  \ast \ \texttt{n}\mapsto\texttt{min} \ \ast \ \texttt{n}\mapsto\texttt{max}
			\end{array}
			\right\}
		}
		\\
		\texttt{insertOp(pn, k, v)}
		\\
		{\color{blue}
			\left\{\exists \ \texttt{t' l r lk1 lk2}. 
			\begin{array}{c}
				\ \texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \\ 
				\ \ast \ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, k))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (k, max))}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specifications of \texttt{inRange} and \texttt{insertOp} for the give-up template}
	\label{fig:insertOp_giveup}
\end{figure}

As previously mentioned, the \texttt{insertOp} specification (Figure \ref{fig:insertOp_giveup}) is slightly different from the lock-coupling version, to account for the added \lstinline{min} and \lstinline{max} fields. In a BST, if the current node's range is \lstinline{(min, max)} and its key is \lstinline{k}, its left child will have range \texttt{(min, k)} and its right child will have range \texttt{(k, max)}. Otherwise, \lstinline{insertOp} behaves identically, storing \lstinline{k} and \lstinline{v} in the current node and creating two empty child nodes.

@@

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% inRange for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn->n}\mapsto\texttt{(t, lock, min, max)} 
			\end{array}
			\right\}
		}
		\\ 
		\texttt{inRange(pn, k)} 
		\\
		{\color{blue}
			\left\{\texttt{res.} \
			\begin{array}{c}
				\ \texttt{pn->n}\mapsto\texttt{(t, lock, min, max)} \  \\ 
				\ \ast  \ \texttt{(if res then } \texttt{(min < k < max)} \texttt{ else } \texttt{(k} \leq \texttt{min} \lor \texttt{k} \geq \texttt{max))}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specifications of \texttt{inRange} and \texttt{insertOp} for the give-up template}
	\label{fig:inRange_giveup}
\end{figure}

The \texttt{inRange} function (Figure \ref{fig:inRange_giveup}) simply computes whether the input key \lstinline{k} is in the range \texttt{(min, max)} associated with the node \texttt{n}, and returns 0 or 1 accordingly.
